### 2020-01-31 introduction.tex
mostly section 3, but touched every section

A common problem in machine learning (ML) 
%and artificial intelligence (AI) 
is to evaluate the quality of a given model.
A popular way to accomplish this
%, in particular in academic environments, 
is to train a model and then evaluate its training and/or testing error.
There are many problems with this approach.
Well-known problems with just examining training/testing curves include that 
they give very limited insight into the overall properties of the model, 
they do not take into account the (often extremely large human and CPU/GPU) time for hyperparameter fiddling,
they typically do not correlate with other properties of interest such as robustness or fairness or interpretability, 
and so on.
A somewhat less well-known problem, but one that is increasingly important (in particular in industrial-scale ML---where the \emph{users} of models are not the \emph{developers} of the models) is that one may access to neither the training data nor the testing data.
Instead, one may simply be given a model that has already been trained---a \emph{pretrained model}---and be told to use it.

Na\"{\i}vely---but in our experience commonly, among both ML practitioners and ML theorists---if one does not have access to training or testing data, then one can say absolutely nothing about the quality of a ML model.
This may be true in worst-case theory, but ML models are used in practice, and there is a need for a \emph{practical theory} to guide that practice.
Moreover, if ML is to become an industrial process, then that process will become siloed: some groups will gather data, other groups will develop models, and still other groups will use those models.
The users of models can not be expected to know the precise details of how the models were built, the specifics of the data that were used to train the model, what was the loss function or hyperparameter values, how precisely the model was regularized, etc.
%
\charles{Moreover, industry faces unique practical problems such as 'do we have enough data for this model?' It is great practical interest to have metrics to evaluate the quality of a ML model in the absence of training and testing data and without any detailed knowledge of the training and testing process.  We seek a theory for pretrained models which can predict how, when, and why such models can be expected to perform well or poorly.}

In this paper, we present and evaluate quality metrics for pretrained neural network (NN) and deep neural network (DNN) models at scale.%
\footnote{We reiterate: One could use these techniques to improve training, and we have been asked about that, but we are not interested in that here. Our main goal here is to use these techniques to evaluate properties of state-of-the-art pretrained NN models.}
To do so, we consider a large suite of hundreds of publicly-available models, mostly from computer vision (CV) and natural language processing (NLP).
%
By now, there are many such state-of-the-art models that are publicly-available, e.g., 
there are now hundreds of pretrained models in CV ($\ge 500$) and NLP ($\approx 100$).%
\footnote{When we began this work in 2018, there were fewer than tens of such models; now in 2020, there are hundreds of such models; and we expect that in a year or two there will be an order of magnitude or more of such models.}
These provide a large corpus of models that by some community standard are state-of-the-art.%
\footnote{Clearly, there is a selection bias or survivorship bias here---people tend not to make publicly-available their poorly-performing models---but these models are things in the world that (like social networks or the internet) can be analyzed for their properties.}
\michael{XXX.  MORE DETAILS.}
Importantly, for all of these models, we have no access to training data or testing data.

\michael{XXX.  LIST PLACES WHERE THEY ARE AVAIALBLE, HERE OR IN NEXT SECTION.}

XXX.  
To do this, we will compute a variety of \emph{quality metrics} based on the spectral properties of the layer weight matrics.
Note that unlike traditional ML approaches, however, \emph{we do not seek a bound on the generalization} (e.g., by evaluating training/test error during training), \emph{we do not seek a new regularizer}, and \emph{we do not aim to evaluate a single model} (e.g., \ncyan{hyperparmeter optimization}). 
Instead, we want to examine different models \ncyan{across} common architecture series, and we want to compare models between different architectures themselves, and in both cases \emph{we aim to predict trends in the quality of pre-trained models without access to training or testing data}.

In more detail, our main contributions are the following.
\begin{itemize}
\item XXX TECHNICAL THING 1
\item XXX TECHNICAL THING 2
\item XXX TECHNICAL THING 3
\item XXX TECHNICAL THING 4
\end{itemize}

>>>>

A common problem in machine learning (ML) 
%and artificial intelligence (AI) 
is to evaluate the quality of a given model.
A popular way to accomplish this
%, in particular in academic environments, 
is to train a model and then evaluate its training and/or testing error.
There are many problems with this approach.
Well-known problems with just examining training/testing curves include that 
they give very limited insight into the overall properties of the model, 
they do not take into account the (often extremely large human and CPU/GPU) time for hyperparameter fiddling,
they typically do not correlate with other properties of interest such as robustness or fairness or interpretability, 
and so on.
A somewhat less well-known problem, but one that is increasingly important (in particular in industrial-scale ML---where the \emph{users} of models are not the \emph{developers} of the models) is that one may have access to neither the training data nor the testing data.
Instead, one may simply be given a model that has already been trained---a \emph{pretrained model}---and be told to use it.

Na\"{\i}vely---but in our experience commonly, among both ML practitioners and ML theorists---if one does not have access to training or testing data, then one can say absolutely nothing about the quality of a ML model.
This may be true in worst-case theory, but ML models are used in practice, and there is a need for a \emph{practical theory} to guide that practice.
Moreover, if ML is to become an industrial process, then that process will become siloed: some groups will gather data, other groups will develop models, and still other groups will use those models.
The users of models can not be expected to know the precise details of how the models were built, the specifics of the data that were used to train the model, what was the loss function or hyperparameter values, how precisely the model was regularized, etc.
%
Moreover, in industry, one faces unique practical problems such as: do we have enough data for this model? 
Methods that are developed and evaluated on any well-defined publicly-available coprus of data, no matter how large or diverse or interesting, are clearly not going to be well-suited to address problems such as this.
It is thus of great practical interest to have metrics to evaluate the quality of a ML model in the absence of training and testing data and without any detailed knowledge of the training and testing process.  
We seek a practical theory for pretrained models which can predict how, when, and why such models can be expected to perform well or poorly.

In this paper, we present and evaluate quality metrics for pretrained neural network (NN) and deep neural network (DNN) models at scale.
To do so, we consider a large suite of hundreds of publicly-available models, mostly from computer vision (CV) and natural language processing (NLP).
%
By now, there are many such state-of-the-art models that are publicly-available, e.g., 
there are now hundreds of pretrained models in CV ($\ge 500$) and NLP ($\approx 100$).%
\footnote{When we began this work in 2018, there were fewer than tens of such models; now in 2020, there are hundreds of such models; and we expect that in a year or two there will be an order of magnitude or more of such models.}
These provide a large corpus of models that by some community standard are state-of-the-art.%
\footnote{Clearly, there is a selection bias or survivorship bias here---people tend not to make publicly-available their poorly-performing models---but these models are things in the world that (like social networks or the internet) can be analyzed for their properties.}
They include 
\michael{XXX, XXX and XXX.  MORE DETAILS.}
\michael{XXX.  LIST PLACES WHERE THEY ARE AVAIALBLE, HERE OR IN NEXT SECTION.}
Importantly, all of these models have been trained by someone else and have been viewed to be of sufficient interest/quality to be made publicly-available, and for all of these models, we have no access to training data or testing data, and we have no knowledge of the training/testing protocols.

The \emph{quality metrics} we consider are based on the spectral properties of the layer weight matrics.
Note that unlike traditional ML approaches, however, \emph{we do not seek a bound on the generalization} (e.g., by evaluating training/test error during training), \emph{we do not seek a new regularizer}, and \emph{we do not aim to evaluate a single model} (e.g., hyperparmeter optimization).% 
\footnote{We reiterate: One could use these techniques to improve training, and we have been asked about that, but we are not interested in that here. Our main goal here is to use these techniques to evaluate properties of state-of-the-art pretrained NN models.}
Instead, we want to examine different models across common architecture series, and we want to compare models between different architectures themselves, and in both cases \emph{we aim to predict trends in the quality of pre-trained models without access to training or testing data}.

In more detail, our main contributions are the following.
\begin{itemize}
\item \michael{XXX TECHNICAL THING 1}
\item \michael{XXX TECHNICAL THING 2}
\item \michael{XXX TECHNICAL THING 3}
\item \michael{XXX TECHNICAL THING 4}
\end{itemize}

### 2020-01-31 methods.tex
mostly section 3, but touched every section

Let us write the Energy Landscape (or optimization function, parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for a typical DNN with $L$ layers, with activation functions $h_{l}(\cdot)$, and with $N\times M$ weight matrices $\mathbf{W}_{l}$ and biases $\mathbf{b}_{l}$, as:
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})  .
\label{eqn:dnn_energy}
\end{equation}
We assume we are given several pretrained Deep Neural Networks (DNNs), e.g., as part of an architecture series.
The models have been trained on (unspecified and unavailable) labeled data $\{d_{i},y_{i}\}\in\mathcal{D}$, using Backprop, by minimizing some (also unspecified and unavailable) loss function $\mathcal{L}()$. 
We expect that most well-trained, production-quality models will employ one or more forms of on regularization, such as Batch Normalization, Dropout, etc., and many will also contain additional structure such as Skip Connections, etc. 
Here, we will ignore these details, and will focus only on the weight matrices.

@@

Each DNN layer contains one or more layer 2D weight matrices $\mathbf{W}_{L}$, and/or 2D feature maps $\mathbf{W}_{i,L}$ extracted from 2D Convolutional layers. 
(For notational convenience, we may drop the $i$ and/or $i,l$ subscripts below.) 
%
\michael{
XXX.  PROBABLY WE DO NOT WANT THE FOLLOWING.  INSTEAD, JUST PRESENT METRICS AND POINT TO PREVIOUS PAPERS FOR JUSTIFICATION.  E.G., WE DONT WANT TO JUSTIFY THE IMPLICIT STATISTICAL INDEPENDENCE ASSUMPTION HERE.  IF OKAY, JUST DELETE THIS RED BLOCK.
We assume the layer weight matrices are statistically independent, allowing us to estimate the Complexity $\mathcal{C}$, or test accuracy, with a standard Product Norm, which resembles a data dependent VC complexity
\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $\mathbf{W}$ is an $(N\times M)$ weight matrix, with $N\ge M$, and 
 $\Vert\mathbf{W}\Vert$ is a matrix norm.   We will actually compute the log Complexity, which takes the form 
of an Average Log Norm:
\begin{eqnarray*}
\log\mathcal{C} &\sim& \log\Vert\mathbf{W}_{1}\Vert+\log\Vert\mathbf{W}_{2}\Vert\cdots\log\Vert\mathbf{W}_{L}\Vert
\end{eqnarray*}
}
%
We have examined a large number of possible quality metrics.
The best performing metrics (recall that we can only consider metrics that do not use training/test data) depend on the norm and/or spectral properties of weight matrices, $\mathbf{W}$.%
\footnote{We do not use intra-layer information from the models in our quality metrics, but as we will describe our metrics can be used to learn about }
We consider the following metrics.
\begin{itemize}
\item 
Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}w^{2}_{i,j} = \sum_{i=1}^{M} \lambda_{i}^{2}$
\michael{Do we use norm or log norm, here and with other norms.  Worth being very explicit and very consistent.}
\item 
Spectral Norm: $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$
\michael{We should probably call the spectral norm $\Vert\mathbf{W}\Vert_{2}$, or change Frob norm notation and have an explicit remork.  Let's decide.}
\item 
Weighted Alpha Metric: $\hat{\alpha}=\alpha\log\lambda_{max}$
\item 
$\alpha$-Norm (or $\alpha$-Shatten Norm): $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda_{i}^{\alpha}$,
\michael{Be clear about how we average this across layers.}
\end{itemize}
The first two metrics are well-known in ML.
The last two deserve special mention.
For all these metrics, $\lambda_{i}$ is the $i^{th}$ eigenvalue of the \emph{Empirical Correlation Matrix},
$ %% $$
\mathbf{X}=\mathbf{W}^{T}\mathbf{W} ,
$ %% $$
and so $\lambda_{max}$ is the maximum eigenvalue of $\mathbf{X}$. 
(These eigenvalues are the squares of the singular values $\sigma_{i}$ of $\mathbf{W}$, i.e., $\lambda_{i}=\sigma^{2}_{i}$.)
For the last two metrics, the exponent $\alpha$ is the power law exponent that arises in the recently-developed \emph{Theory of Heavy Tailed Self Regularization (HT-SR)}~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Operationally, $\alpha$ is determined by using the publicly-available \emph{WeightWatcher} tool (\cite{weightwatcher_package}) to fit the Empirical Spectral Density (ESD) of $\mathbf{X}$, i.e., a histogram of the eigenvalues, call it $\rho(\lambda)$, to a truncated power law
\begin{equation}
\rho(\lambda)\sim\lambda^{\alpha},\;\;\lambda\le\lambda_{max}  .
\end{equation}
\michael{We need to be clear that this is a truncated power law fit and that $\lambda_{max}$ comes from that and not the largest empirical eigenvalue.}
The Weighted Alpha Metric was introduced previously~\cite{MM20_SDM}, where (on a much smaller set of data than we consider here) it was shown to correlate well with the trends in reported test accuracies of pretrained DNNs.
Based on this, here we introduce and evaluate the $\alpha$-Norm metric.
One would expect $\hat{\alpha}$ to approximate the log $\alpha$-Norm very well for $\alpha < 2$ and reasoably well for $\alpha\in[2,5]$~\cite{MM20_unpub_work}.

\michael{Need to say that such large $\alpha$ values don't mean much.}

\michael{Need to highlight difference between $\alpha$ and $\hat{\alpha}$.}

@@

\paragraph{XXX.}
XXX.  THIS VERIFICATION IS NOT ABOUT CONV LAYERS, IT IS ABOUT PL MORE GENERALLY, CORRECT?  WE SHOULD CLARIFY AND SQUISH.
To verify that our approach is meaningful, we need to confirm that the ESD is neither due to a random matrix, nor due to unsually large matrix elements, but, in fact, captures correlations learned from the data. 
We examine typical layer for the pretained AlexNet model (distributed with pyTorch). 
Figure~\ref{fig:alexnet1} displays the ESD for the first slice (or matrix $\mathbf{W}$) of the third Conv2D layer, extracted from a 4-index Tensor of shape $(384, 192, 3, 3)$.  The red line displays the best fit to a random matrix, using the Marchenko pastur theory~\cite{MM}.  We can see the random matrix model does not describe the ESD very well. For comparison, Figure \ref{fig:alexnet2} shows the ESD of the same matrix, randomly shuffled; here looks similar to the red line plot of the orginal ESD.  In fact, the empircal ESD is better modeled with a truncated power law distribtion.
\michael{We may want to give a one-sentence summary of this par and fig at the end of the previous par.}

\begin{figure}[H]
   \centering
   \subfigure[Actual ESD]{
     %\includegraphics[scale=0.5]{img/alexnet1.png} 
     \includegraphics[scale=0.25]{img/alexnet1.png} 
     \label{fig:alexnet1}
   }
   \subfigure[ESD of randomly shuffled matrix]{
      %\includegraphics[scale=0.5]{img/alexnet2.png}
      \includegraphics[scale=0.25]{img/alexnet2.png}
      \label{fig:alexnet2}
   }
   \caption{ESD of AlexNet Conv2D pre-Activation map for Layer 3 Slice 1, actual and randomized.
            \michael{Need better figs here.}
           }
   \label{fig:alexnet}
\end{figure}

Although the ESD is \emph{Heavy Tailed}, this does not imply that the orginal matrix $\mathbf{W}$ is itself heavy tailed--only the correlation matrix $\mathbf{X}$ is. 
If $\mathbf{W}$ was, then it would contain 1 or more unusually large matrix elements, and they would dominate the ESD.  
Of course the randomized $\mathbf{W}$ would also be heavy tailed, but its ESD neither resembles the original nor is it heavy tailed. 
So we can rule out $\mathbf{W}$ being heavy tailed.
\michael{These comments seem out of place, since they hold more generally than for the Conv2D layers.}

These plots tell us that the pre-activation maps of the Conv2D contains significant correlations learned from the data.  
By modeling the ESD with a power law distribution $\lambda^{\alpha}$, we can characterize the amount of correlation learned;
the smaller the exponent $\alpha$, the more correlation in the weight matrix. 
\michael{These comments seem out of place, since they hold more generally than for the Conv2D layers.}

@@

\michael{MOVE TO LATER: COMMENT ON HOW LOG NORM first and last layers behave, maybe somewhere else.}

\michael{CMOVE TO LATER: OMMENT ON HOW LOG PORM  for GPT includes unusually high alpha, not meaningful other than to show the trend.}

@@

We compute the metrics using the WeightWatcher tool (version 0.2.7), and we provide Jupyter notebooks in the github repo for this paper~\cite{repo}, making the results fully reproducible.

\michael{XXX.  FEW SENTENCES ABOUT REPRODUCIBILITY MORE GENERALLY HERE.}

>>>>

Let us write the Energy Landscape (or optimization function, parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for a typical DNN with $L$ layers, with activation functions $h_{l}(\cdot)$, and with $N\times M$ weight matrices $\mathbf{W}_{l}$ and biases $\mathbf{b}_{l}$, as:
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})  .
\label{eqn:dnn_energy}
\end{equation}
We assume we are given several pretrained Deep Neural Networks (DNNs), e.g., as part of an architecture series.
The models have been trained on (unspecified and unavailable) labeled data $\{d_{i},y_{i}\}\in\mathcal{D}$, using Backprop, by minimizing some (also unspecified and unavailable) loss function $\mathcal{L}(\cdot)$. 
We expect that most well-trained, production-quality models will employ one or more forms of on regularization, such as Batch Normalization, Dropout, etc., and many will also contain additional structure such as Skip Connections, etc. 
Here, we will ignore these details, and will focus only on the weight matrices.

@@

Each DNN layer contains one or more layer 2D weight matrices $\mathbf{W}_{L}$, and/or 2D feature maps $\mathbf{W}_{i,L}$ extracted from 2D Convolutional layers. 
(For notational convenience, we may drop the $i$ and/or $i,l$ subscripts below; and we let $\mathbf{W}$ be a generic $N\times M$ weight matrix, with $N\ge M$.) 
%
We have examined a large number of possible quality metrics.
The best performing metrics (recall that we can only consider metrics that do not use training/test data) depend on the norm and/or spectral properties of weight matrices, $\mathbf{W}$.%
\footnote{We do not use intra-layer information from the models in our quality metrics, but as we will describe our metrics can be used to learn about that.}
We consider the following metrics.
\begin{itemize}
\item 
Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\sum_{i,j}w^{2}_{i,j} = \sum_{i=1}^{M} \lambda_{i}^{2}$
\item 
Spectral Norm: $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$
\item 
Weighted Alpha Metric: $\hat{\alpha}=\alpha\log\lambda_{max}$
\item 
$\alpha$-Norm (or $\alpha$-Shatten Norm): $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda_{i}^{\alpha}$
\end{itemize}
The first two metrics are well-known in ML.
The last two deserve special mention.
For all these metrics, $\lambda_{i}$ is the $i^{th}$ eigenvalue of the \emph{Empirical Correlation Matrix},
$ %% $$
\mathbf{X}=\mathbf{W}^{T}\mathbf{W} ,
$ %% $$
and so $\lambda_{max}$ is the maximum eigenvalue of $\mathbf{X}$. 
(These eigenvalues are the squares of the singular values $\sigma_{i}$ of $\mathbf{W}$, i.e., $\lambda_{i}=\sigma^{2}_{i}$.)
For the last two metrics, the exponent $\alpha$ is the power law exponent that arises in the recently-developed \emph{Theory of Heavy Tailed Self Regularization (HT-SR)}~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Operationally, $\alpha$ is determined by using the publicly-available \emph{WeightWatcher} tool (\cite{weightwatcher_package}) to fit the Empirical Spectral Density (ESD) of $\mathbf{X}$, i.e., a histogram of the eigenvalues, call it $\rho(\lambda)$, to a truncated power law
\begin{equation}
\rho(\lambda)\sim\lambda^{\alpha},\;\;\lambda\le\lambda_{max}  .
\end{equation}
\michael{We need to be clear that this is a truncated power law fit and that $\lambda_{max}$ comes from that and not the largest empirical eigenvalue.}
The Weighted Alpha Metric was introduced previously~\cite{MM20_SDM}, where (on a much smaller set of data than we consider here) it was shown to correlate well with the trends in reported test accuracies of pretrained DNNs.
Based on this, here we introduce and evaluate the $\alpha$-Norm metric.
One would expect $\hat{\alpha}$ to approximate the log $\alpha$-Norm very well for $\alpha < 2$ and reasoably well for $\alpha\in[2,5]$~\cite{MM20_unpub_work}.

Each of these metrics is defined for a given layer $\mathbf{W}$ matrix.
For the Weighted Alpha Metric, we consider the average of $\hat{\alpha}$ over all layers, i.e., $\sum_l \hat{\alpha}_l = \sum_l \alpha_l\log\lambda_{max,l} $ .  
\michael{Be careful to get that right.}
For the norm-based metrics, we consider the average of the log of the norm to the appropriate power.
For example, for the $\alpha$-Norm, we compute 
\begin{equation}
\label{eqn:sum_log_alpha_norm_alpha}
\sum\nolimits_l \log \Vert\mathbf{W}_l\Vert_{\alpha_l}^{\alpha_l} 
=
\sum\nolimits_l \alpha_l \log \Vert\mathbf{W}_l\Vert_{\alpha_l} .
\end{equation}
Informallly, this amounts to assuming that the layer weight matrices are statistically independent, in which case we can estimate the model complexity $\mathcal{C}$, or test accuracy, with a standard Product Norm (which resembles a data dependent VC complexity),
\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert \times \cdots \times \Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $\Vert\cdot\Vert$ is a matrix norm.   
In this case, the log Complexity takes the form of an Average Log Norm,
\begin{equation}
\label{eqn:eqn:sum_log_norm}
\log\mathcal{C} \sim \log\Vert\mathbf{W}_{1}\Vert+\log\Vert\mathbf{W}_{2}\Vert + \cdots + \log\Vert\mathbf{W}_{L}\Vert  .
\end{equation}
For the Frobenius and Spectral norms, we can use Eqn.~(\ref{eqn:eqn:sum_log_norm}) directly. 
For example, when taking $\log\Vert\mathbf{W}_{l}\Vert_{F}^{2}$, the $2$ comes down and out of the sum, and thus ignoring it only changes the metric by a constant factor.
For the Weighted Alpha Norm, however, $\alpha_l$ varies from layer to layer, and so in Eqn.~(\ref{eqn:sum_log_alpha_norm_alpha}) it cannot be taken out of the sum.

@@

@@

@@

We compute the metrics using the WeightWatcher tool (version 0.2.7), and we provide Jupyter notebooks in the github repo for this paper~\cite{repo}, making the results fully reproducible.
\michael{XXX.  FEW SENTENCES ABOUT REPRODUCIBILITY MORE GENERALLY HERE, HERE OR IN DISCUSSION/CONCLUSION.}

### 2020-01-31 nlp_models.tex
mostly section 3, but touched every section

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
GPT & 49 & 1.64  & 1.72 & 7.01 & 7.28 \\
GPT (small) & 49 & 2.04  & 2.54& 9.62 & 9.87 \\
GPT2 medium & 98 & 2.08 & 2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 & 1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 & 1.92 & 7.17 & 7.51 \\
\hline
\end{tabular}
\end{center}
\caption{Average Log Norm Metrics for pretrainnd OpenAI GPT and GPT2 models.}
\label{table:nlp}
\end{table}

>>>>

%        &  Num.  & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{2}$ & $\hat{\alpha}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
% Series & Models & Metric                     & Metric                     & Metric         & Metric                                   \\

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
\hline
%   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
% Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
        & Num.   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
 Series & Layers & Metric                     & Metric                          & Metric         & Metric                                   \\
\hline
GPT & 49 & 1.64  & 1.72 & 7.01 & 7.28 \\
GPT (small) & 49 & 2.04  & 2.54& 9.62 & 9.87 \\
GPT2 medium & 98 & 2.08 & 2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 & 1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 & 1.92 & 7.17 & 7.51 \\
\hline
\end{tabular}
\end{center}
\caption{Average value for each of the four metrics for pretrainnd OpenAI GPT and GPT2 models.}
\label{table:nlp}
\end{table}
